The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-10-14 paper.tex
Added to Chapter on repeater networks.

\sihui{
\subsection{Repeater networks}
}

>>>>

\sihui{
\subsection{Repeater networks}
Quantum repeaters are devices that distribute entanglement across a network, or teleport quantum states between nodes of a network. The purpose of such a quantum network is to communicate and process quantum information over long distances. While photons serve as great medium for such information transfer, many implementations of photonic repeat network require some kind of nonlinear interactions involving cavities. [talk about DLCZ, requiring quantum memories or feedforwarding \cite{bib:Azuma15} (not require memories but...)\cite{bib:Ewert17}]
}
